Backscatter Modulation Design for Symbiotic Radio Networks

### 2021-11-26 main.tex
:dizzy: Information functions

	\begin{section}{The Multi-Tag Case}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019e}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

@@

			To explicitly specify the content of backscatter symbol vector, we label it by the corresponding modulation index set. For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k \colon k \in \mathcal{K}\}$ and the backscatter symbol vector as $\bar{\boldsymbol{c}}_{m_{\mathcal{K}}} \triangleq [\bar{c}_{m_1},\ldots,\bar{c}_{m_K}]^T \in \mathcal{C}^{K \times 1}$. Since any $\bar{\boldsymbol{c}}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $\boldsymbol{m}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the backscatter symbol vector in status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks. Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal. The corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
				\label{eq:detection_threshold}
			\end{equation}

			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
				\label{eq:decision_region}
			\end{equation}
			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$. Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
				\label{eq:energy_distribution}
			\end{equation}
			where $\Gamma(\cdot)$ is the gamma function. As such, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				p(z_j \mid \bar{\boldsymbol{c}}_i) = p(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:equivalent_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				p(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} p(z_j \mid \bar{\boldsymbol{c}}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} p(z_j \mid \bar{\boldsymbol{c}}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:equivalent_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
		\end{subsection}
	\end{section}

	\begin{section}{Precoder and Tag Input Design}
		TODO
	\end{section}

	\begin{section}{The Single-tag Case}
		% \begin{figure}[!t]
		% 	\centering
		% 	\def\svgwidth{0.9\columnwidth}
		% 	\import{assets/}{symbiotic_radio.pdf_tex}
		% 	\caption{A single-user single-tag symbiotic radio system.}
		% 	\label{fi:symbiotic_radio}
		% \end{figure}
		As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary AP-UE downlink system, the AP transmits to the single-antenna user. In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient. Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$. We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging. One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019e}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}. Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP. Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$. At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020a}.}
		\begin{equation}
			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
		\end{equation}
		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise. We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.

>>>>

	\begin{section}{The Multi-Tag Case}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-user (UE) multi-tag (TG) symbiotic radio network where the RF signal generated by the $Q$-antenna Access Point (AP) is shared by two coexisting systems. In the primary downlink system, the AP transmits information to the single-antenna user. In the secondary backscatter system, the AP acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated RF signals, and the user serves as the multi-tag backscatter reader. Denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the AP-TG $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the TG $k$-UE backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient Channel State Information at the Transmitter (CSIT) acquisition can be challenging. One possible approach is that the AP sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

@@

			To explicitly specify each backscatter symbol combination, we label it by the corresponding modulation index set. For tag $k$ at state $m_k$, $\forall k \in \mathcal{K}$, we define the modulation index set as $m_{\mathcal{K}} \triangleq \{m_k : k \in \mathcal{K}\}$ and the tag input combination as $\bar{c}_{m_{\mathcal{K}}} \triangleq \{\bar{c}_{m_k} : k \in \mathcal{K}\}$. Since any $\bar{c}_{m_{\mathcal{K}}}$ remains constant per $N$ primary symbols, the received signal at block $n$ is only subject to the variation of the primary source $s[n]$ and AWGN $w[n]$, and thus follows CSCG distribution $y_{m_{\mathcal{K}}}[n] \sim \mathcal{CN}\left(0,\sigma_{m_{\mathcal{K}}}^2\right)$ with variance
			\begin{equation}
				\sigma_{m_{\mathcal{K}}}^2 \triangleq \Bigl\lvert \bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H \bar{c}_{m_k}\bigr) \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2,
				\label{eq:receive_variance}
			\end{equation}
			which denotes the expectation of the received power per primary block under tag modulation index set $\boldsymbol{m}$, and can be numerically evaluated based on the precoder, tag, channel, and noise knowledge. For the ease of exposition, we sort all possible $\sigma_{m_{\mathcal{K}}}^2$ in ascending order by a one-to-one mapping $\boldsymbol{m} \mapsto i$, denote the hypothesis that the tag input combination at status $i$ as $\mathcal{H}_i$, and define $\sigma_i^2 \le \sigma_j^2$ for $i < j$, $i,j \in \mathcal{M^K} \triangleq \{1,\ldots,M^K\}$.\footnote{When more than one modulation index sets yield the same energy level, the mapping is not unique and the detection fails to separate them. This blind spot issue can be mitigated by multi-antenna techniques.} For the optimal Maximum-Likelihood (ML) detector, the likelihood ratio between hypotheses $\mathcal{H}_i$ and $\mathcal{H}_j$ is \cite{Qian2019}
			\begin{equation}
				\Lambda_{i,j}(\boldsymbol{y}) = \frac{f(\boldsymbol{y} \mid \mathcal{H}_i)}{f(\boldsymbol{y} \mid \mathcal{H}_j)} = \left( \frac{\sigma_j^2}{\sigma_i^2} \right)^N \exp \left( \frac{\sigma_i^2 - \sigma_j^2}{\sigma_i^2 \sigma_j^2} z \right),
				\label{eq:likelihood_ratio}
			\end{equation}
			where $f(\boldsymbol{y} \mid \mathcal{H}_i)$ and $f(\boldsymbol{y} \mid \mathcal{H}_j)$ are respectively the conditional probability density function of receiving $\boldsymbol{y}$ under hypothesis $\mathcal{H}_i$ and $\mathcal{H}_j$, and $z \triangleq \lVert \boldsymbol{y} \rVert^2$ is the received signal energy over $N$ primary blocks. Obviously, the likelihood ratio only depends on $z$ and the energy detection is thus optimal. The corresponding decision rule is
			\begin{equation}
				\Lambda_{i,j}(z) \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} 1 \iff z \underset{\mathcal{H}_j}{\overset{\mathcal{H}_i}{\lessgtr}} T_{i,j},
				\label{eq:decision_rule}
			\end{equation}
			where the detection threshold between $\mathcal{H}_i$ and $\mathcal{H}_j$ is
			\begin{equation}
				T_{i,j} \triangleq N \frac{\sigma_i^2 \sigma_j^2}{\sigma_i^2 - \sigma_j^2} \log \frac{\sigma_i^2}{\sigma_j^2}.
				\label{eq:detection_threshold}
			\end{equation}

			Accordingly, the decision region of hypothesis $\mathcal{H}_i$ is
			\begin{equation}
				\mathcal{R}_i \triangleq [T_{i-1, i}, T_{i, i+1}),
				\label{eq:decision_region}
			\end{equation}
			and we manually define $T_{0,1} \triangleq 0$ and $T_{M^K,M^K+1} \triangleq \infty$. Let $f(z \mid \mathcal{H}_i)$ be the conditional probability density function of receiving $z$ under hypothesis $\mathcal{H}_i$. Since $z$ follows chi-squared distribution with $2N$ degrees of freedom, it holds that
			\begin{equation}
				f(z \mid \mathcal{H}_i) = \frac{z^{N-1} e^{-z/\sigma_i^2}}{\sigma_i^{2N} \Gamma(N)},
				\label{eq:energy_distribution}
			\end{equation}
			where $\Gamma(\cdot)$ is the gamma function. As such, we can formulate an equivalent point-to-point discrete memoryless channel from tag input combination alphabet $\mathcal{M^K}$ to received energy level alphabet $\mathcal{M^K}$ as a transition matrix, where the probability of observing energy level $j$ under tag input combination $i$ is\footnote{For simplicity, we assume there exists at least one feasible precoder that produces distinct received energy levels for all tag input combinations. [TODO] Is this necessary? Maybe we can keep those same energy levels and avoid them by input distribution design.}
			\begin{equation}
				P(z_j \mid \bar{c}_i) = P(z \in \mathcal{R}_j \mid \mathcal{H}_i) = \int_{\mathcal{R}_j} f(z \mid \mathcal{H}_i) \dd z.
				\label{eq:equivalent_channel}
			\end{equation}

			Based on the equivalent point-to-point channel \eqref{eq:equivalent_channel}, we can compute the marginal probability on all tags and obtain $K$ transition matrices from $\mathcal{M}$ to $\mathcal{M^K}$ that compose a discrete memoryless MAC. Mathematically speaking, the probability of observing energy level $j$ when tag $k$ at status $m_k$ is
			\begin{equation}
				P(z_j \mid c_k = \bar{c}_{m_k}) = \frac{\sum_{m_{\mathcal{K} \setminus k}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{\sum_{m_{\mathcal{K}}} P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}.
				\label{eq:mac}
			\end{equation}

			In summary, for every possible tag input combination, the expected power of the received signal per block can be evaluated by \eqref{eq:receive_variance}, the energy detection threshold to nearby states can be computed by \eqref{eq:detection_threshold}, the decision region can be retrieved by \eqref{eq:decision_region}, the equivalent point-to-point channel can be obtained by \eqref{eq:energy_distribution} and \eqref{eq:equivalent_channel}, and the discrete memoryless MAC can be extracted by \eqref{eq:mac}.
		\end{subsection}

		\begin{subsection}{Backscatter sum-capacity}
			Before investigating the sum-capacity of the tags, we introduce some definitions in information theory. Following \cite{Rezaeian2004}, the information function associated with individual tag input combination $\bar{c}_{m_{\mathcal{K}}}$ is defined as
			\begin{equation}
				% I(\bar{c}_{m_{\mathcal{K}}} ; z) = \infdiv*{P(z \mid \bar{c}_{m_{\mathcal{K}}})}{P(z)}
				I(\bar{c}_{m_{\mathcal{K}}} ; z) \triangleq \sum_j P(z_j \mid \bar{c}_{m_{\mathcal{K}}}) \log \frac{P(z_j \mid \bar{c}_{m_{\mathcal{K}}})}{P(z_j)},
				\label{eq:information_function}
			\end{equation}
			and the marginal information function on $\mathcal{S} \subset \mathcal{K}$ is thus
			\begin{equation}
				I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{m_{\mathcal{K} \setminus \mathcal{S}}} P_{m_{\mathcal{K} \setminus \mathcal{S}}}(\bar{c}_{m_{\mathcal{K} \setminus \mathcal{S}}}) I(\bar{c}_{m_{\mathcal{K}}} ; z).
			\end{equation}
			On top of this, the mutual information and marginal mutual information can be expressed respectively as
			\begin{align}
				I(c_{\mathcal{K}} ; z)
				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z)\right],\\
				I(c_{\mathcal{S}} ; z)
				& = \mathbb{E}_{c_{\mathcal{S}}} \left[I(\bar{c}_{m_{\mathcal{S}}} ; z)\right].
			\end{align}

			% \begin{equation}
			% 	I_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}} ; z) = \sum_{\mathcal{S}^c} P_{\mathcal{S}^c}(\bar{c}_{m_{\mathcal{S}^c}}) I(\bar{c}_{m_{\mathcal{K}}} ; z),
			% \end{equation}
			% where $\mathcal{S}^c \triangleq \mathcal{K} \setminus \mathcal{S}$.

			% and the mutual information can be expressed as
			% \begin{equation}
			% 	I(\boldsymbol{c} ; z) = \mathbb{E}_{\boldsymbol{c}}
			% \end{equation}

			% function that evaluates the information associated with individual

			Denote the input probability distribution of tag $k$ at status $m_k$ as $r_k(\bar{c}_{m_k})$.

			% For $\mathcal{S} \subset \mathcal{K}$, denote the input probability distribution that user $r_{\mathcal{S}}(\bar{c}_{m_{\mathcal{S}}})$
		\end{subsection}
	\end{section}

	\begin{section}{Tag Input and Precoder Design}
		In this section, we exploit tag input and precoder design to characterize the achievable region of the primary rate and the backscatter sum-rate.
		\begin{subsection}{Backscatter sum-rate}

		\end{subsection}
	\end{section}

	\begin{section}{The Single-tag Case}
		% \begin{figure}[!t]
		% 	\centering
		% 	\def\svgwidth{0.9\columnwidth}
		% 	\import{assets/}{symbiotic_radio.pdf_tex}
		% 	\caption{A single-user single-tag symbiotic radio system.}
		% 	\label{fi:symbiotic_radio}
		% \end{figure}
		As shown in Fig.~NULL, we propose a single-user (UE) single-tag (TG) symbiotic radio network where the RF signal generated by the single-antenna Access Point (AP) is shared by two coexisting systems. In the primary AP-UE downlink system, the AP transmits to the single-antenna user. In the secondary AP-TG-UE backscatter system, the AP acts as the carrier emitter, the user serves as the backscatter reader, and the single-antenna tag modulates its information over the reradiated RF signal by varying the reflection coefficient. Denote the AP-UE direct channel as $h_{\mathrm{D}}$, the AP-TG forward channel as $h_{\mathrm{F}}$, and the TG-UE backward channel as $h_{\mathrm{B}}$. We consider the quasi-static block fading model and assume the CSI of the direct channel and the cascaded forward-backward channel $h_{\mathrm{C}} \triangleq h_{\mathrm{B}} h_{\mathrm{F}}$ are known at the AP.\footnote{Due to the lack of RF chains at the passive tag, accurate and efficient CSI acquisition at the AP can be challenging. One possible approach is that the AP sends known pilots, the tag responds in a pre-defined manner, and the user performs least-square estimation then feeds back to the AP \cite{Bharadia2015,Yang2015b,Guo2019g}.} It is assumed that the primary symbol $s$ follows standard CSCG distribution $\mathcal{CN}(0,1)$ and the secondary symbol $c$ employs $M$-PSK modulation by \eqref{eq:backscatter_modulation}. Due to the practical constraints on switching speed and synchronization gap, the passive tag typically transmits at a much lower data rate than the AP. Hence, we assume the secondary symbol period is $N \gg 1 \in \mathbb{Z}_{++}$ times the primary symbol period and focus on the interval of one particular $c$. At (primary) symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$, the user simultaneously captures the signal from both primary and secondary links as\footnote{We assume the time difference of arrival from the AP-UE path and the AP-TG-UE path are negligible compared to the symbol period \cite{Guo2019b,Liang2020,Long2020b}.}
		\begin{equation}
			y[n] = \sqrt{P} h_{\mathrm{D}} s[n] + \sqrt{\alpha P} h_{\mathrm{C}} c s[n] + w[n],
		\end{equation}
		where $P$ is the average transmit power at the AP and $w \sim \mathcal{CN}(0,\sigma^2)$ is the additive white Gaussian noise. We also define $\boldsymbol{y} \triangleq \bigl[y[1],\ldots,y[N]\bigr]^T$.
